SVG: The Paper

### 2022-07-04 Analysis/index.Rmd
rerunning

```{r}
# try doing per trial
a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60)  ->timedat

>>>>

```{r}
# try doing per trial
a %>% select(observer, condition, trial, found, selected_max) %>%
  full_join(d, by = c("observer", "condition", "trial", "found")) %>%
  group_by(observer, condition, trial) %>%
  summarise(time_taken = max(RT),
            acc = mean(selected_max, na.rm = T), 
            .groups = "drop") %>%
  filter(time_taken < 60) -> timedat
